---
title: "bad markdown"
author: "Candace Savonen"
date: "2023-02-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

These examples are from https://www.markdownguide.org/basic-syntax/ 

# Here's a Heading

Try to put a blank line before...

# Heading


No blank lines before and after this heading might not work out. 
# Heading
Don't do this!

#Here's a Heading


Some words and now the heading won't be at the start of the line # Heading

Don't put tabs or spaces in front of your paragraphs.

Keep lines left-aligned like this.

    This can result in unexpected formatting problems.

  Don't add tabs or spaces in front of paragraphs.
  
  
First line with two spaces after.    
And the next line.

First line with the HTML tag after.<br>
And the next line.

First line with a backslash after.\
And the next line.

First line with nothing after.
And the next line.


Love**is**bold

Love__is__bold


A*cat*meow	

A_cat_meow


This is really***very***important text.	

This is really___very___important text.



Try to put a blank line before...

> This is a blockquote

...and after a blockquote.


Without blank lines, this might not look right.
> This is a blockquote
Don't do this!


1. First item
2. Second item	


1) First item
2) Second item



- First item
- Second item
- Third item
- Fourth item	



+ First item
* Second item
- Third item
+ Fourth item

This text right here is going to mess up the below list
- First item
- Second item
- Third item
- Fourth item	


Try to put a blank line before...

---

...and after a horizontal rule.	



Without blank lines, this would be a heading.
---
Don't do this!


[link](https://www.example.com/my%20great%20page)

<a href="https://www.example.com/my great page">link</a>


[link]
(https://www.example.com/my great page)



```{r cars}
summary(cars)
```

```{r pressure}
plot(pressure)
```

